# Things To Remember

## Question 1

Likelihood function: summation of log f(x) where theta changes, do for each x value

```{r}
# SAMPLING BETWEEN TWO VALUES
runif(100, min = -pi, max = pi)
```

## Question 2

```{r}
# PLOT A HISTOGRAM AND SUPERIMPOSE
ggplot(weighted_function, aes(x=y))+
  geom_histogram(aes(y = ..density..), color = "black") +  
  geom_density(color = "red", size = 1.2) 
```

**Superimposing** a density function on a histogram" means to visually overlay a smooth curve representing a probability density function (PDF) on top of a bar chart (histogram) of your data

## Question 3

```{r}
# LINE FROM ORIGIN TO POINTS USING GEOM_SEGMENT
ggplot(two_dimensions, aes(x=U1, y=U2))+
  geom_point() +
  geom_segment(aes(x=0, y=0, xend =U1, yend=U2), color="red")

# SUM EACH ROW
x <- matrix()
rowSums(x)
```

## Question 4

For U1 and U2 from uniform distributions. Then $z_1 = \sqrt{-2logU}cos(2\pi V)$ and $z_2 = \sqrt{-2logU}sin(2\pi V)$ (note repeateable pattern of cos and sin if had U3, U4, ...).

Therefore the chi distribution can be estimated using $z_1^2 + z_2^2 + ...$

```{r}
# SORT A VECTOR
c <- 1:5
sort(c, decreasing = TRUE)
```

## Question 5

```{r}
# TO INVERT A MATRIX USE "SOLVE"
```
